\section{Future Work}

Due to time constraints, we were unable to modify Speculative Paxos to run on a cloud platform and thus were unable to reproduce this comparison from the original NOPaxos paper. We leave it to future work to conduct such an experiment and gather more data on the applicability of network-reliant consensus protocols on cloud platforms. 

Additionally, we were able to experiment only marginally with varying the maximum batch size for the closest competitor of NOPaxos in this paper (Paxos with Batching), choosing ultimately to use the same maximum batch size as was used in the original NOPaxos paper. Our initial experiments showed that increasing or decreasing this maximum batch size noticeably changed the performance of Paxos with Batching with regards to NOPaxos. Although exploring the trade-offs of different batch sizes is beyond the scope of this paper, we encourage future investigations in this area.  

An area that we did not explore in this paper was the performance of NOPaxos and other consensus protocols across different cloud platforms. In particular, there are some (more expensive, less popular) cloud platforms that do allow multicast, the software implementation of which led to a bottleneck in our experiments. A very worthwhile future project would be investigating whether on such a platform, the results of the original paper could be more closely replicated, or if other currently obscured bottlenecks or issues would arise. 

We also mentioned briefly our decision to put all cloud compute nodes in the same geographic location for testing purposes, as doing otherwise severely impacted the throughput and latency it was possible to achieve, and we wanted to test at levels comparable to those in the original paper. However, the ability to provide georeplication is a significant advantage of cloud platforms. It remains an open question whether the latency improvements NOPaxos is able to achieve when nodes are in the same location are still significant (and reproducible) when nodes are distributed across different locations, or if such microsecond-level latencies become undetectable in the presence of greater delays.

Finally, as previously mentioned, we have left further optimization of the sequencer (the current bottleneck of NOPaxos on a cloud platform), to future work, as such improvements require innovation and investment beyond the scope of this paper. 
